\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=0.5cm,
    bottom=0.7cm,
    left=1cm,
    right=1cm,
    footskip=0.5cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Abhishek Singh's Resume},
    pdfauthor={Abhishek Singh},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi
\usepackage{charter}

\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.10cm}
\pagenumbering{gobble}

% Tighter section title spacing
\titleformat{\section}{\needspace{2\baselineskip}\bfseries\normalsize}{}{0pt}{}[\vspace{0.5pt}\titlerule]
\titlespacing{\section}{-1pt}{0.20cm}{0.10cm}

% Tighter bullet list spacing
\newenvironment{highlights}{
    \begin{itemize}[topsep=0.05cm, parsep=0.05cm, partopsep=0pt, itemsep=0pt, leftmargin=10pt]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0cm}{0cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.2cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.2}
}{
    \par\kern\topsep
}

%--------------------------- Document Starts ------------------------

\begin{document}
\newcommand{\AND}{\unskip\cleaders\copy\ANDbox\hskip\wd\ANDbox\ignorespaces}
\newsavebox\ANDbox
\sbox\ANDbox{$|$}

\begin{header}
    \fontsize{18pt}{18pt}\selectfont Abhishek Singh

    \vspace{0.05cm}
    \normalsize

    \mbox{\href{mailto:abhisheksdtu@gmail.com}{\color{black}{\footnotesize\faEnvelope[regular]}\hspace*{0.12cm}abhisheksdtu@gmail.com}}%
    \kern 0.17cm%
    \AND%
    \kern 0.17cm%
    \mbox{\href{tel:+916388913980}{\color{black}{\footnotesize\faPhone*}\hspace*{0.12cm}+91 6388913980}}%
    \kern 0.17cm%
    \AND%
    \kern 0.17cm%
    \mbox{{\color{black}\footnotesize\faMapMarker*}\hspace*{0.12cm}Gurgaon, India}%
    \kern 0.17cm%
    \AND%
    \kern 0.17cm%
    \mbox{\href{https://linkedin.com/in/abhisheksdtu}{\color{black}{\footnotesize\faLinkedinIn}\hspace*{0.12cm}abhisheksdtu}}%
    \kern 0.17cm%
    \AND%
    \kern 0.17cm%
    \mbox{\href{https://github.com/abhisheksdtu}{\color{black}{\footnotesize\faGithub}\hspace*{0.12cm}abhisheksdtu}}%
\end{header}

%---------- Education ---------
\section{Education}
\begin{twocolentry}{2018 -- 2022}
    \textbf{Delhi Technological University}, B.Tech
\end{twocolentry}

%---------- Technologies (in two columns) ----------
\section{Technologies}

\begin{onecolentry}
	\textbf{Coding Languages:} Java, Go, Python\\
        \vspace{0.05cm}
	\textbf{Databases:} PostgreSQL, ScyllaDB, ElasticSearch\\
        \vspace{0.05cm}
	\textbf{Technologies:} Spring, Spring Boot, Hibernate, JUnit, IBatis, Redis, Pulsar, Docker, Kubernetes, SonarQube\\
        \vspace{0.05cm}
	\textbf{Others:} Git, Swagger, Postman, REST, Microservices, Event Driven Architecture, Kibana
\end{onecolentry}

%---------- Experience ----------
\section{Professional Experience}

\begin{twocolentry}{Jun 2022 -- Present}
    \textbf{Software Engineer}, \textit{Sirion}
\end{twocolentry}
\begin{onecolentry}
    \begin{highlights}
        \item Developed and maintained core backend features using Java Spring Boot, contributing to scalable and robust product development.
        \item Designed system architectures, including high-level and low-level components, to support scalable and maintainable solutions.
        \item Collaborated with the frontend team to integrate backend services, ensuring seamless user experience across multiple platforms.
        \item Ensured high code quality with 80\% test coverage, leveraging Test-Driven Development (TDD) practices.
        \item Implemented CI/CD pipelines using Jenkins, resulting in faster deployment.
        \item Mentored junior developers and conducted code reviews, fostering a culture of collaboration.
    \end{highlights}
\end{onecolentry}

\vspace{0.08cm}

\begin{twocolentry}{Dec 2021 -- May 2022}
    \textbf{Software Engineering Intern}, \textit{IntelloLabs}
\end{twocolentry}
\begin{onecolentry}
    \begin{highlights}
        \item Developed and implemented automated scripts using Python for web crawling of websites and mobile apps.
        \item Utilized web scraping libraries and techniques to efficiently extract and collect data from sources.
        \item Participated in daily stand-up meetings, sprint planning, and release tracker sessions as part of an Agile development team, ensuring timely and efficient progress.
        \item Utilized Git for version control and JIRA for task tracking to facilitate collaboration and project management.
    \end{highlights}
\end{onecolentry}

%---------- Projects ----------
\section{Projects}

\begin{onecolentry}
    \textbf{Webhook Service}, \textit{Sirion}
    \begin{highlights}
        \item \textbf{Technologies Used:} Java, Spring Boot, Apache Pulsar, Redis, Cassandra
        \item Developed a scalable webhook microservice for managing event-driven communications, enabling dynamic webhook registrations, event processing, and delivery retries.
        \item Integrated Apache Pulsar for event streaming, providing reliable delivery of events, and used Redis for rate limiting and distributed locks.
        \item Created robust custom retry mechanisms for failed webhook deliveries, along with alerting systems for prolonged failures.
        \item Designed and implemented REST APIs for webhook registration, updates, and deregistration with comprehensive validation and error handling.
        \item Collaborated with cross-functional teams to design validation rules for webhook triggers and implemented monitoring features for webhook failures.
    \end{highlights}
\end{onecolentry}

\vspace{0.05cm}

\begin{onecolentry}
    \textbf{B2B API Framework}, \textit{Sirion}
    \begin{highlights}
        \item \textbf{Technologies Used:} Java, Spring Boot, PostgreSQL
        \item Designed and developed a B2B API framework for managing Sirion entities.
        \item Built generic CRUD APIs to support create, read, update, and delete operations for various entities, providing flexibility and extensibility.
        \item Created metadata and field options APIs to dynamically manage entity fields, including fetching available options for both static and custom fields.
        \item Developed search APIs to retrieve entities with selected fields, filters, and pagination, ensuring efficient data listing and retrieval.
    \end{highlights}
\end{onecolentry}

\vspace{0.05cm}

\begin{onecolentry}
    \textbf{Compliance Framework}, \textit{Sirion}
    \begin{highlights}
        \item \textbf{Technologies Used:} Java, Spring Boot, PostgreSQL, Pulsar
        \item Developed a compliance-as-a-service tool enabling users to create surveys and view responses on the monolith.
        \item Seamlessly integrated multiple survey platforms to connect large scale multi-source data.
        \item Created Sirion's own survey app providing features such as survey templates, uploads, schedules, emails, responses, and reporting.
        \item Implemented data synchronization between microservice and main app for real-time updates.
    \end{highlights}
\end{onecolentry}

\end{document}